---
title: "MyLabJournal"
output: html_document
---

<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 10px;
}

</style>

<div class="row" style="padding-top: 30px;">
<div class="col-sm-6">

# **Kamal Abdelrahman's Lab Journal**

#Practice Problems

##Easy

###1) Do simple math with numbers, addition, subtraction, multiplication, division
```{r, eval=TRUE}
#Addition with numbers
1 + 1

#Subtraction with numbers
1 - 1

#Multiply with numbers
10 * 1

```

###2) Put numbers into variables, do simple math on the variables
```{r, eval=TRUE}
#Addition with variables
a <- 1 

b <- 1 

a + b 

#Subtraction with variables
a <- 1 

b <- 1

a - b

#Multiply with variables
a <- 10

b <- 1

a * b 

#Divide with variables
a <- 20

b <- 2

a/b
```

###2) Put numbers into variables, do simple math on the variables
```{r, eval=TRUE}
#Addition with variables
a <- 1 

b <- 1 

a + b 

#Subtraction with variables
a <- 1 

b <- 1

a - b

#Multiply with variables
a <- 10

b <- 1

a * b 

#Divide with variables
a <- 20

b <- 2

a/b
```

###3) Write code that will place the numbers 1 to 100 separately into a variable using for loop
```{r, eval=TRUE}

 
for (i in 1:100) { #i will start at 1
 a <- i #that value will be stored in a
        #This is repeated as long as i is not greater than 100
 print(a) #Prints a, an array of numbers
} 
```

###3a) Then, again using the seq function.
```{r, eval=TRUE}

#Starts from 1
#Increases by 2 to 100
b <- seq(1, 100, 2 ) 
```

### 4) Find the sum of all the integer numbers from 1 to 100.
```{r, eval=TRUE}

Sum <- 0 #Declare and intialize "Sum""

for(i in o) { # For the length of "o" (50)
 Sum <- Sum + i # Sum equals the value of the previous iteration on 
}

print(Sum) # Prints the final sum value

```

