---
title: "MyLabJournal"
output: html_document
---

<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 10px;
}

</style>

<div class="row" style="padding-top: 30px;">
<div class="col-sm-6">

# **Kamal Abdelrahman's Lab Journal**

#Practice Problems

##Easy

###1) Do simple math with numbers, addition, subtraction, multiplication, division
```{r, eval=TRUE}
#Addition with numbers
1 + 1

#Subtraction with numbers
1 - 1

#Multiply with numbers
10 * 1

```

###2) Put numbers into variables, do simple math on the variables
```{r, eval=TRUE}
#Addition with variables
a <- 1 

b <- 1 

a + b 

#Subtraction with variables
a <- 1 

b <- 1

a - b

#Multiply with variables
a <- 10

b <- 1

a * b 

#Divide with variables
a <- 20

b <- 2

a/b
```


###3) Write code that will place the numbers 1 to 100 separately into a variable using for loop
```{r, eval=TRUE}

 
for (i in 1:100) { #i will start at 1
 a <- i #that value will be stored in a
        #This is repeated as long as i is not greater than 100
 print(a) #Prints a, an array of numbers
} 
```

###3a) Then, again using the seq function.
```{r, eval=TRUE}

#Starts from 1
#Increases by 2 to 100
b <- seq(1, 100, 2 ) 
print(b)
```

### 4) Find the sum of all the integer numbers from 1 to 100.
```{r, eval=TRUE}

Sum <- 0 #Declare and intialize "Sum""

for(i in b) { # For the length of "o" (50)
 Sum <- Sum + i # Sum equals the value of the previous iteration on 
}

print(Sum) # Prints the final sum value
sum(b) #Check with sum function
```

### 5) Write a function that adds two values.
```{r, eval=TRUE}

#Function "addition" will take in two values "x" (1) and "y" (2)
#Prints the value from the function "addition"

addition <- function(x, y) {
  x + y
}
print(addition(1,2))
```

### 6) List all of the odd numbers from 1 to 100.
```{r, eval=TRUE}

for (i in 1:100) {
  if (i %% 2 ==1) 
    print(i)
}

```

### 7) List all of the prime numbers from 1 to 1000.
```{r, eval=TRUE}


```

### 8) Print 100 values
```{r, eval=TRUE}

runif(100)

```

### 9) Print 100 random numbers within a specific range
```{r, eval=TRUE}

runif(100, 0 , 1000)

```

### 10) Write a functions for the mean, median, mode, range, and standard deviation
```{r, eval=TRUE}
#Mean
Mean <- function(x){
  sum(x)/length(x)
}

x <- c(1,2,3,4,5,6)
Mean(x)

#Median

#Mode
Mode <- function(x) {
 ux <- unique(x)
 ux[which.max(tabulate(match(x, ux)))]
}

x <- c(1,2,3,3,3)
Mode(x)

#Range

Range <- function(x) {
  max(x) - min(x)
}

x <- c(1,2,3,3,3)
Range(x)

#Standard Deviation

StandardDev <- function(x) {
  sqrt(sum((x- sum(x)/length(x))^2/(length(x)-1)))
}

x<- c(1,2,3,4)
StandardDev(x)

sd(c(1,2,3,4))

```


### 11) Count the number of characters in a string variable
```{r, eval=TRUE}

letters <- "abcdefghijk"
lettersnew <- strsplit(letters,split="")

lettersnew
nchar(letters, type = "chars")
```

### 12) Count the number of words in a string variable
```{r, eval=TRUE}

sentence <- "This sentence will be seperated"
sentencesnew <- strsplit(sentence,split=" ")

sentencesnew
sapply(sentencesnew, length)
```

### 13) Count the number of sentences in a string variable (MARK)
```{r, eval=TRUE}

sentences <- "This sentence will be seperated. This sentence will also be seperated."
sentencessplit <- strsplit(sentences,split = ".")

sentencessplit
sapply(sentencessplit, length)
```

### 14) Count the number of times a specific character occurs in a string variable
```{r, eval=TRUE}
library(stringr)
string <- c("a", "b", "c", "d", "a", "b", "c", "d")

sum(str_count(string, pattern = "a"))

```

### 15) Do a logical test to see if one word is found within the text of another string variable (MARK)
```{r, eval=TRUE}

word <- "word"
sentence <- "There is a word"
sentence2 <- c("There", "is", "a", "word")

word%in%sentence
word%in%sentence2
```


### 16) Print the computer time in milliseconds
```{r, eval=TRUE}

print(as.numeric(Sys.time())*1000, digits=15)
```
### 17) Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time
```{r, eval=TRUE}
start.time <- Sys.time()

Sum <- 0

for (i in c(1:100)){
  Sum = Sum + i
}

Sum

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```

### 18) Read a .txt file or .csv file into a variable
```{r, eval=FALSE}
datatxt <- read.txt("\Pathway\filename.txt")
datacsv <- read.csv("\Pathway\filename.csv")
```

### 19) Output the contents of a variable to a .txt file
```{r, eval=FALSE}
write.csv("variable", "pathway")
```

### 20) Create a variable that stores a 20x20 matrix of random numbers
```{r, eval=TRUE}
a <- matrix(sample(1:400, 400), ncol=20,nrow=20)
a
```

### 21) Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values
```{r, eval=FALSE}
write.txt(variable, pathway, sep = "," or "\t", dec = ".")
```

##Hard

### 1) List the numbers from 1 to 100 with the following constraints. If the number can be divided by three evenly, then print Fizz instead of the number. If the number can be divided by five evenly, then print Buzz instead of the number. Finally, if the number can be divided by three and five evenly, then print FizzBuzz instead of the number. (MARK)
```{r, eval=FALSE}
for (i in as.numeric(c(1:100))){
  if ((i %% 3 == 0) & (i %% 5 == 0)) {
      print(i)
  }
  else if (i %% 3 == 0) {
  print("Fizz")
  }
  else if (i %% 5 == 0)  {
  print("Fizz")
  }
}
```






