---
title: "Sample Problems"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


#Input and output


```{r, eval=TRUE}
#Gives description of an R topic. Usually includes a definition, general code, example of application
help() - 

help("mean")

```

```{r, eval=TRUE}
#Gives a description of an R topic

?

?median

```

```{r, eval=TRUE}

#Lists the local variables of a function
ls()  

x <- c(1,2,3,4)
y <- c(5,6,7,8)

data <- data.frame(x,y)
ls(data)

```

```{r, eval=TRUE}
#Returns the name of files in a filepath

dir() 

dir("/Applications")

```

```{r, eval=TRUE}

#Returns the name of files in a filepath 
list.files()

list.files("/Applications")

```


#Input and Output
```{r, eval=TRUE}
wd()


```

```{r, eval=TRUE}
save()

```

```{r, eval=TRUE}
load()

```

```{r, eval=TRUE}
#Returns a list of datasets already included in R

data() 

data() # Loads general list of datasets
data("mtcars") # Loads a specific dataset 
```

```{r, eval=TRUE}
#Loads a package to be used in an R program

library() 

#Load ggplot2 package

library(ggplot2)
```

```{r, eval=TRUE}
# Loads a table into R

read.table()

```



```{r, eval=FALSE}
#Exports a variable to a file as a data frame

write.table() 


```

#Data Creation
```{r, eval=FALSE}
#Indicates what values to included in a function. These could be column indeces or values.

from:to (where from and to are replaced with numbers, e.g. 1:10)  

c(1:10)


```

```{r, eval=TRUE}
#Generates a standard pattern from beginning to end, by a standard increase or decrease

seq(1,100,5) 


```

```{r, eval=TRUE}
#Repeats arguments in the given order, for a number of iterations

rep()  

rep(1:10,2)

```

```{r, eval=TRUE}
#Converts variables into a data frame

data.frame() 

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

z
```

```{r, eval=TRUE}
#Converts variables into a data frame

list() 

```

```{r, eval=TRUE}
#Creates a matrix, a set that contains at least

matrix()  

```

```{r, eval=TRUE}
#Converts an object to factor class  


x <- c("Male", "Female", "Male", "Female")

class(x)

factor(x)
```

```{r, eval=TRUE}
#Converts an object to factor class  

rbind() Combines vector, matrix or data frame by rows
a <- (1:5)
b <- (6:10)
c <- data.frame(a,b)

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

rbind(c,z)
```

```{r, eval=TRUE}
#Combines vector, matrix or data frame by columns 

cbind() 
a <- (1:5)
b <- (6:10)
c <- data.frame(a,b)

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

cbind(c,z)
```







Slicing and extracting data
indexing vectors 

##Variable conversion
```{r, eval=TRUE}
#Combines vector, matrix or data frame by columns 

as.data.frame(x) 

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

z
```

```{r, eval=TRUE}
#Combines vector, matrix or data frame by columns 

as.data.frame(x) 

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

z
```

```{r, eval=TRUE}
#Combines vector, matrix or data frame by columns 

as.data.frame(x) 

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

z
```

```{r, eval=TRUE}
#Combines vector, matrix or data frame by columns 

as.data.frame(x) 

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

z
```

```{r, eval=TRUE}
#Converts varabiable to numeric data type

x <- c("1","2","3","4")

class(x)

as.numeric(x) 
```

```{r, eval=TRUE}
#Converts variable to a logical data type

x <- c("T", "F", "T", "F")

class(x)

as.logical(x) 
```

```{r, eval=TRUE}
#Converts varaiable to character data type

x <- c(1, 2, 3, 4)

class(x)

as.character(x) 
```

##Variable information
```{r, eval=TRUE}
#Determines if variable is "NA" value. Returns True or False.

is.na() 
```

```{r, eval=TRUE}
#Determines if value is undefined. Returns True or False

is.null() 
```

```{r, eval=TRUE}
#Determines if value is a dataframe Returns True or False

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

is.data.frame(z)
```

```{r, eval=TRUE}
#Determines if value is a numeric data type. Returns True or False.

x <- (1:5)

is.numeric(x) 
```

```{r, eval=TRUE}
#Determines if value is a numeric data type. Returns True or False.

x <- c("1", "2", "3")

is.numeric(x) 
```

```{r, eval=TRUE}
#Determines if value is a character data type. Returns True or False.

x <- c("1", "2", "3")

is.character(x) 
```


```{r, eval=TRUE}
#Determines length of value

x <- c(1:100)

length(x) 
```

```{r, eval=TRUE}
#Gets or sets the length of a vector (list) or other objects

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

dim(x)
```

```{r, eval=TRUE}
#Identifies the number of rows in x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

nrow(x) 
```

```{r, eval=TRUE}
#Identifies data type of variable

x <- c("First", "Second", "Third")

class(x)  
```

```{r, eval=TRUE}
#Accesses the attribute of an object attribute

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

attributes(x)
```

#Data selection and manipulation
```{r, eval=TRUE}
#Accesses the attribute of an object attribute

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

attributes(x)
```

```{r, eval=TRUE}
#Identifies index that has the lowest value in a variable

which.min(c(32,34,3,2,212,33243,34234,532))
```

```{r, eval=TRUE}
#Identifies index that has the highest value in a variable

which.min(c(32,34,3,2,212,33243,34234,532))
```

```{r, eval=TRUE}
#Identifies index that has the highest value in a variable

which.min(c(32,34,3,2,212,33243,34234,532))
```

```{r, eval=TRUE}
#Identifies index of an argument that fulfills a condition

x <- c(20,3,2, 4,30,2,3,5,32,432)
which(x > 100)

```

```{r, eval=TRUE}
#Arranges a vector in either descending or ascending order

x <- c(20,3,2, 4,30,2,3,5,32,432)

sort(x,decreasing = F)
```

```{r, eval=TRUE}
#Returns unique values of an argument

x <- c(1,1,1,1,1,1,2,2,2,2,2,2,2,23,3,3,3,3,33,3,3)

unique(x)
```



table() - Creates a table of frequency counts of categorical variables

sample() - Takes a sample of the specified size from the elements of x

##Math
```{r, eval=TRUE}
#Identifies maximum value of a set of values

max(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies minimum value of a set of values

max(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies range of a set of values

range(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies sum of a set of values

sum(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies mean of a set of values

mean(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies median of a set of values

median(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies variance of a set of values

var(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#Identifies correlation of a set of values

cor(c(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23), c(1,2,23,3,4,4,5,5,6,7,4,3,3,2,3,5,6))  
```

```{r, eval=TRUE}
#Identifies absolute value

abs(-100 + 0) 
```

##Matrix
```{r, eval=TRUE}
#Returns the sum from each row of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

rowSums(x)
```



t()
diag()

```{r, eval=TRUE}
#Returns the sum from each column of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

colSums(x)
```

```{r, eval=TRUE}
#Returns the mean from each row of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

rowMeans(x)
```

```{r, eval=TRUE}
#Returns the mean from each column of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

colMeans(x)
```

<!-- ##Advanced Data processing -->
<!-- ```{r, eval=TRUE} -->
<!-- #Returns the mean from each column of x -->

<!-- apply() -->
<!-- aggregate() - Group data by a specific group -->
<!-- ``` -->

##Strings

```{r, eval=TRUE}
#Converts argument to character data type and concatentates them together

paste(1,2,3,4,5)
```

```{r, eval=TRUE}
#Splits character vector x into substrings by matching substring

strsplit("BR_OOK_LYN_CO_LL_EGE", "_")
```

```{r, eval=TRUE}
#Splits character vector x into substrings by matching substring

strsplit("BR_OOK_LYN_CO_LL_EGE", "_")
```

```{r, eval=TRUE}
#Converts text to lower case

tolower("LOWERCASE")  
```

```{r, eval=TRUE}
#Converts text to lower case

toupper("uppercase")  
```

```{r, eval=TRUE}
#Base histogram plot

x <- rnorm(100, 45, 2)
hist(x)
```

```{r, eval=TRUE}
#Plots a regular baseplot based on the type and number of vairables

x <- rnorm(100, 45, 2)
y <- rnorm(100, 45, 2)
plot(x,y) 
```

##Distributions
```{r, eval=TRUE}
#Plots a regular baseplot based on the type and number of vairables

x <- rnorm(100, 45, 2)
y <- rnorm(100, 45, 2)
plot(x,y) 
```



rnorm() - Create a normal distribution 
runif() - Creates a distribution based on sample, and min/max values


Programming

show that you can define a function

addition <- function(x,y)
 x + y

addition(1,2)

show that you can write a for loop

for i in c(1:100)

show that you can write a while loop

i <- 1
while(i < 10) {
 i = i + 1
 print(i)
}

show that you can write an if else statement

x = 1
y = 2
if(x = 3) {
 print(x)
} else {
 print(y) 
}


