---
title: "MyLabJournal"
output: html_document
---

<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 10px;
}

</style>

<div class="row" style="padding-top: 30px;">
<div class="col-sm-6">

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE, eval = FALSE)
```


#General Bits
```{r, eval=TRUE}
#help() - Gives description of an R topic. Usually includes a definition, general code, example of application

help(mean)

```

```{r, eval=TRUE}
#? - Gives a description of an R topic

?median

```

```{r, eval=FALSE}
#ls() - Lists variables in the environment

ls()

```

```{r, eval=FALSE}
#dir() - Lists files in default directory

dir()

```

```{r, eval=FALSE}
#list.files() - Lists files in default directory

list.files()

```



#Input and Output
```{r, eval=FALSE}
#save() - Saves files in R

save(file)
```

```{r, eval=FALSE}
#load() - Loads a file in R

load(file)
```

```{r, eval=TRUE}
#data() - Loads a dataset from R

data()
```

```{r, eval=TRUE}
#library() - Loads a package to be used in an R program

library(ggplot2)
```

```{r, eval=FALSE}
#read.table() - Reads a file into table in R

read.table(file)
```

```{r, eval=FALSE}
#read.csv() - Reads a csv file into table in R

read.csv(file)
```

```{r, eval=FALSE}
#scan() - Read data into a vector or list from the console or file

x <- scan()
x

```


```{r, eval=TRUE}
#print() - Prints an argument

print("This was printed")
```

```{r, eval=TRUE}
#cat() -  function prints the objects, concatenates the representations

x <- "EGG"
y <- "PERSON"

cat(x,y)
```

```{r, eval=FALSE}
#write.table() - Writes a variable as a table in to file

x <- sample(c(1:100), 100)

write(x, pathway)
```

#Data Creation
```{r, eval=TRUE}
#c() - Concatenates values, variables together

x <- (1:10)
y <- (11:20)

c(x,y)
```

```{r, eval=TRUE}
#from:to - Creates a list of numbers at from a starting value to an ending value.

1:10

```

```{r, eval=TRUE}
#seq() - Generates a standard pattern from beginning to end, by a given increment or decrement

seq(1,100,5) 


```


```{r, eval=TRUE}
#rep() - Repeats arguments in the given order, for a number of iterations

rep(1:10,2)

```

```{r, eval=TRUE}
#data.frame() - Converts variables into a data frame

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

z
```

```{r, eval=TRUE}
#list() <- Creates a vector list of variables

list("A", "B", "C", "D") 

```

```{r, eval=TRUE}
#matrix() - Creates a matrix, a set that contains at least

matrix(c(1:6),nrow=3,ncol=2)

```

```{r, eval=TRUE}
#factor() - Converts an object to factor class  

x <- c("Male", "Female", "Male", "Female")

factor(x)
class(factor(x))
```

```{r, eval=TRUE}
#rbind() - Combines vector, matrix or data frame by rows
x <- matrix(c(1:6),nrow=3,ncol=2,byrow=TRUE)
y <- matrix(c(1:6),nrow=3,ncol=2,byrow=TRUE)

rbind(x,y)
```

```{r, eval=TRUE}
#cbind() - Combines vector, matrix or data frame by columns 

#cbind() 
x <- matrix(c(1:6),nrow=3,ncol=2,byrow=TRUE)
y <- matrix(c(1:6),nrow=3,ncol=2,byrow=TRUE)

cbind(x,y)
```

##Variable conversion
###Indexing Vectors
```{r, eval=TRUE}
#x[n] - nth element

x <- sample(c(1:100), 10)
x
x[2]

```

```{r, eval=TRUE}
#x[-n] - All but nth element

x <- sample(c(1:10), 10)
x
x[-2]

```

```{r, eval=TRUE}
#x[(1:n)] elements from n+1 to the end


x <- sample(c(1:10), 10)
x
x[(1:4)] 

```

```{r, eval=TRUE}
#x[-(1:n)] - Elements from n+1 to the end

x <- sample(c(1:10), 10)
x
x[-(1:4)]

```

```{r, eval=TRUE}
#x[c(n, n, n)] - Specific n elements


x <- sample(c(1:10), 10)
x
x[c(1,2,10)] 

```

```{r, eval=TRUE}
#x[“name”] - Elements named “name”


x <- rep(c("X", "Y"), 2)
x
x["X"] 

```

```{r, eval=TRUE}
#x[x>n] - All elements greater than n

x <- 1:10
x
x[x>4] 

```

```{r, eval=TRUE}
#x[x > n1 & x < n2] - All elements greather than n1 and less than n2

x <- 1:10
x
x[x>4 & x < 8] 

```

```{r, eval=TRUE}
#x[x %in% c(“a”,“and”,“the”)] - All elements in given set

x <- 1:10
x
x[x %in% c(1, 2, 10, 30)]

```

###Indexing lists
```{r, eval=TRUE}
#x[n] - List with elements n

x <- list("First", "Second", "Third")
x
x[2]

```

```{r, eval=TRUE}
#x[[n]] - nth element of the list

x <- list("First", "Second", "Third")
x
x[[1]]

```

```{r, eval=TRUE}
#x[[“name”]] - Element of the list named “name”

x <- list("First", "Second", "Third")
x
x[["First"]]

```

```{r, eval=TRUE}
#x$name - Id

x <- list("First", "Second", "Third")
x
x$"First"
```

###Indexing Matrices
```{r, eval=TRUE}
#x[a,b] - Element at row a, column b

x <- matrix(c(1:9),nrow=3,ncol=3)
x
x[3,2]
```

```{r, eval=TRUE}
#x[i,] - Row a

x <- matrix(c(1:9),nrow=3,ncol=3)
x
x[1,]
```

```{r, eval=TRUE}
#x[,b] - Column b

x <- matrix(c(1:9),nrow=3,ncol=3)
x
x[,2]
```

```{r, eval=TRUE}
#x[,c(1,2)] - columns 1 and 3

x <- matrix(c(1:9),nrow=3,ncol=3)
x
x[,c(1,3)]
```

```{r, eval=TRUE}
#x[“name”,] - Row named “name”

x <- matrix(c(1:9),nrow=3,ncol=3)
x
x[1,]
```

###Indexing data frames (matrix indexing plus the following)
```{r, eval=TRUE}
#x[“name”,] - Column named “name”

x <- (1:3)
y <- (4:6)
z <- data.frame(x,y)
z
z["x"]

```

```{r, eval=TRUE}
#x$nameid - Column name 

x <- (1:3)
y <- (4:6)
z <- data.frame(x,y)
z
z$x

```

##Variable conversion

```{r, eval=TRUE}
#as.data.frame() - Converts variable to a dataframe

x <- c(1:5)
x
as.data.frame(x)
```

```{r, eval=TRUE}
#as.numeric() - Converts variable to numeric data type

x <- c("1","2","3","4")

class(x)

class(as.numeric(x)) 
```


```{r, eval=TRUE}
#Converts variable to a logical data type

x <- c("T", "F", "T", "F")

class(x)

as.logical(x) 
```

```{r, eval=TRUE}
#Converts varaiable to character data type

x <- c(1, 2, 3, 4)

class(x)

as.character(x) 
```

##Variable information
```{r, eval=TRUE}
#is.na() - Determines if variable is "NA" value. Returns True or False.

x <- NA
is.na(x)

```

```{r, eval=TRUE}
#is.null() - Determines if value is undefined. Returns True or False

j <- NULL
is.null(j)

k <- 1
is.null(k) 

```

```{r, eval=TRUE}
#Determines if value is a dataframe Returns True or False

x <- (1:5)
y <- (6:10)
z <- data.frame(x,y)

is.data.frame(z)
```

```{r, eval=TRUE}
#Determines if value is a numeric data type. Returns True or False.

x <- c(1,2,3)

is.numeric(x) 

y <- c("1", "2", "3")

is.numeric(y) 
```

```{r, eval=TRUE}
#Determines if value is a character data type. Returns True or False.

x <- c("1", "2", "3")

is.character(x) 
```

```{r, eval=TRUE}
#Determines length of value

x <- c(1:100)

length(x) 
```

```{r, eval=TRUE}
#Gets or sets the length of a vector (list) or other objects

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

dim(x)
```

```{r, eval=TRUE}
#dimnames() - Dimension names of an object

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

dimnames(x) 
```

```{r, eval=TRUE}
#nrow() - Identifies the number of rows in x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

nrow(x) 
```

```{r, eval=TRUE}
#ncol() - Identifies the number of columns in x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

ncol(x) 
```


```{r, eval=TRUE}
#Identifies data type of variable

x <- c("First", "Second", "Third")

class(x)  
```

```{r, eval=TRUE}
#Accesses the attribute of an object attribute

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE)

attributes(x)
```

#Data selection and manipulation
```{r, eval=TRUE}
#which.max() - Identifies index that has the highest value in a variable

which.max(c(32,34,3,2,212,33243,34234,532))
```


```{r, eval=TRUE}
#which.min() - Identifies index that has the lowest value in a variable

which.min(c(32,34,3,2,212,33243,34234,532))
```

```{r, eval=TRUE}
#which() - Identifies index of an argument that fulfills a condition

x <- c(20,3,2, 4,30,2,3,5,32,432)
which(x > 100)
```

```{r, eval=TRUE}
#sort() - Arranges a vector in either descending or ascending order

x <- c(20,3,2, 4,30,2,3,5,32,432)

sort(x,decreasing = F)
```

```{r, eval=TRUE}
#unique() = Returns unique values of a variable

x <- c(1,1,1,1,1,1,2,2,2,2,2,2,2,23,3,3,3,3,33,3,3)

unique(x)
```

```{r, eval=TRUE}
#table() - Converts a variable into a table and counts the frequency of its unique values

x <- c(1,1,1,1,1,1,2,2,2,2,2,2,2,23,3,3,3,3,33,3,3)

table(x)
```

```{r, eval=TRUE}
#sample() - Creates a random sample of numbers, letters, etc.

x <- sample(1:10, 10)

x
```

##Math
```{r, eval=TRUE}
#max()- Identifies maximum value of a set of values

max(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#min() - Identifies minimum value of a set of values

min(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#range() - Identifies range of a set of values

range(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#sum() -Identifies sum of a set of values

sum(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#mean() - Identifies mean of a set of values

mean(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#median() - Identifies median of a set of values

median(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23)  
```

```{r, eval=TRUE}
#var() - Identifies variance of a set of values

var(c(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23))  
```

```{r, eval=TRUE}
#sd() - Identifies standard deviation of a set of values

sd(c(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23))  
```

```{r, eval=TRUE}
#cor() - Identifies correlation of a set of values

cor(c(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23), c(1,2,23,3,4,4,5,5,6,7,4,3,3,2,3,5,6))  
```

```{r, eval=TRUE}
#round() - Rounds a value to a given place

cor(c(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23), c(1,2,23,3,4,4,5,5,6,7,4,3,3,2,3,5,6))
round((cor(c(1,2,4,5,6,9,12,12,43,2,1,2,3,2,1,2,23), c(1,2,23,3,4,4,5,5,6,7,4,3,3,2,3,5,6))), 2)
```

```{r, eval=TRUE}
#abs() - Identifies absolute value

abs(-100 + 0) 
```

##Matrices
```{r, eval=TRUE}
#t() - Transposes a dataframe or matrix

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x
t(x)
```

```{r, eval=TRUE}
#diag() - Diagonal matrix of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=3,byrow=TRUE) 

x
diag(x)
```

```{r, eval=TRUE}
#colSums() - Returns the sum from each row of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

colSums(x)
```

```{r, eval=TRUE}
#Returns the mean from each row of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

rowMeans(x)
```

```{r, eval=TRUE}
#Returns the mean from each column of x

x <- matrix(c(3,5,7,1,9,4),nrow=3,ncol=2,byrow=TRUE) 

x

colMeans(x)
```


##Advanced Data Processing
```{r, eval=TRUE}
#aaply() - Apply a function on multiple cases at once

a <- c(T, F, T)
b <- c(1,2,3)
c <- c("First", "Second", "Third")

d <- data.frame(a,b,c)
apply(d, c(1,2), class)

```

```{r, eval=TRUE}
#aggregate() - Takes an aggregate of a given set of values

Score <- sample(c(1:100), 10)
Gender <- sample(c("Boy", "Girl"), 10, replace = T)
FinalGrades <- data.frame(Score,Gender)
aggregate(Score ~ Gender, FinalGrades, mean)

```

##Strings
```{r, eval=TRUE}
#paste() - Concatenate vectors after converting to character.

b <- 1:10

c <- paste(b)
b
c

```

```{r, eval=TRUE}
#strsplit() - Splits character vector x into substrings by matching substring

strsplit("BR_OOK_LYN_CO_LL_EGE", "_")
```

```{r, eval=TRUE}
#tolower() - Converts text to lower case

tolower("LOWERCASE")  
```

```{r, eval=TRUE}
#toupper() - Converts text to lower case

toupper("uppercase")  
```

##Plotting
```{r, eval=TRUE}
#hist() - Base histogram plot

x <- rnorm(100, 45, 2)
hist(x)
```

```{r, eval=TRUE}
#plot() - Plots a regular baseplot based on the type and number of vairables

x <- rnorm(100, 45, 2)
y <- rnorm(100, 45, 2)
plot(x,y) 
```

##Distributions
```{r, eval=TRUE}
#rnorm() - Compute a series of values that would make a normal distribution

x <- rnorm(100, 45, 2)
x
```

```{r, eval=TRUE}
#runif() - Compute a series of values within a range

x <- runif(100, 45, 2)
x
```

##Programming
```{r, eval=TRUE}
#Function

SelfSquare <- function(x){
  x <- x * x
}

print(SelfSquare(4))
```

```{r, eval=TRUE}
#For loop

for (i in c(1:5)){
  print(i)
}
```

```{r, eval=TRUE}
#While loop
i <- 1
while(i <= 5){
  print(i)
  print("i is less than or equal to 5")
  i <- i +1
}
```

```{r, eval=TRUE}
#If else 
i <- 6
if (i <= 5){
  print(i)
  print("i is less than or equal to 5")
} else {
  print(i)
  print("i is greater than 5")
}
```

```{r, eval=TRUE}
#return() - Sends back a value from within a function in regards to it's function

addition <- function(x){
  if (x > 5){
    return(x +1)
  } else{
    return(x +2)
  }
}
addition(1)
addition(10)


```

```{r, eval=TRUE}
#break() - Usually used in while loops to fall out of the loop

i <- 1
while(i <= 5){
  print(i)
  print("i is less than or equal to 5")
  i <- i +1
  if(i == 3){
    print(i)
    print("Here is where the loop will break")
    break
  }
}
```



